Density-dependent selection in evolutionary genetics: a lottery model of Grime's triangle

### 2017-04-04 manuscript.tex
latest

\section*{•}

@@

>>>>

\section*{Selection and population density under cyclical birth and death rates}

We now consider periodically varying birth and death rates, as could occur due to seasonal cycles. For example, natural \textit{Drosophila} populations expand rapidly in the warmer months when fruit is abundant,  and are carried through the colder months by a much smaller number of dormant individuals. Population density undergoes seasonal cycles, and within these cycles, hundreds of polymorphisms also cycle in frequency, some of which may potentially have been doing so for millions of years \citep{bergland_14}.

Figure \ref{fluctuatingselection} shows the behavior of Eq. \eqref{eq:master} for an example where $b$ and $d$ cycle between zero and positive values (``summers'' with rapid growth and no mortality, and ``winters'' with positive mortality and no growth).

Selection alternatively favors the $b$ specialist

. However, due to the storage effect neither has an advantage over a full environemntal cycle, and

@@

\begin{figure}
\centering
\includegraphics[scale=0.7]{fluctuatingselection.pdf}
\caption{\label{fig:fluctuatingselection} Stable coexistence between $b$ and $d$ specialists when $b$ and $d$ fluctuate. (a) $b$ (solid lines) and $d$ (dashed lines) alternate being nonzero. The $b$ specialist (black) has higher $b$ and $d$ than the $d$ specialist (blue). (b) Both types grow during the positive $b$ phase, and decline during the positive $d$ phase, but the $d$ specialist (blue) does so at a slower rate than the $b$ specialist (black). Total height (blue+black) is population size $N$. (c) The positive $b$ and $d$ phases favor the $b$ and $d$ specialists, respectively, and they stably coexist due to the storage effect.} 
\end{figure}
